A simulation model of DNA methylation data

### 2015-04-06 Rmarkdown/methsim.Rmd
Complete describing implementation of meths

`methsim` is written in R and builds on the `MethylationTuples` package described in __CHAPTER__, as well as key R packages available on Bioconductor and CRAN (see `DESCRIPTION` for a complete list. __TODO: Add citations of all packages used in thesis__).

@@

The next step is to simulate a 'true' methylome by applying the `simulate()` method to the `SimulateMethylomeParam` object. This returns a `SimulatedMethylome`, a schematic of which is __SHOWN BELOW__.

>>>>

`methsim` is written in R and builds on the `MethylationTuples` package described in __CHAPTER__, as well as several R packages available on Bioconductor and CRAN (see `DESCRIPTION` for a complete list. __TODO: Add citations of all packages used in thesis__).

@@

The next step is to simulate a 'true' methylome by applying the `simulate()` method to the `SimulateMethylomeParam` object. This returns a `SimulatedMethylome`, a schematic of which is __SHOWN BELOW__. The `SimulatedMethylome` object forms part of the `SimulateBSParam` object from which a `SimualtedMethylome` is created by calling the `simulate()` method.
